\section{Conclusion}
  \label{sec:conclusion}

  Step~3 of the Admissibility Sub-Programme is now complete.
  The chain of implications is:
  \[
    \text{neutral generators}
    \;\Longrightarrow\;
    \text{pairwise character geometry}
    \;\Longrightarrow\;
    \text{finite subgroup structure}.
  \]
  Specifically:
  \begin{enumerate}
    \item The Gram identity (Lemma~\ref{lem:gram-identity}) encodes axis geometry in
    character values.
    \item The second-moment tensor (Proposition~\ref{prop:dic-anisotropy}) detects
    the dihedral case by anisotropy.
    \item The orthogonal-block lemma (Lemma~\ref{lem:orth-implies-Q8}) identifies $Q_8$.
    \item The structural exclusion of $2T$ (Proposition~\ref{prop:2T-excluded}) removes
    the tetrahedral case.
    \item The main theorem (Theorem~\ref{thm:gram-rigidity}) assembles the complete
    classification~\eqref{eq:admissible-list}.
  \end{enumerate}
  Together with SpectralAdmissibility~1.0 and SpectralCapacity~1.0, this establishes
  the full picture: the substrate groups compatible with bounded-flux spectral
  neutrality are exactly $Q_8$, $\mathrm{Dic}_n$ ($n \ge 3$), $2O$, and $2I$.

  \begin{thebibliography}{9}

    \bibitem{Klein1876}
    F.~Klein,
    \textit{Vorlesungen \"uber das Ikosaeder und die Aufl\"osung der Gleichungen vom
    f\"unften Grade},
    Teubner, Leipzig, 1884.

    \bibitem{SpectralAdmissibility}
    \textit{SpectralAdmissibility~1.0} --- Step~1 of the Admissibility Sub-Programme,
    companion note.

    \bibitem{SpectralCapacity}
    \textit{SpectralCapacity~1.0} --- Step~2 of the Admissibility Sub-Programme,
    companion note.

    \bibitem{Cosmochrony}
    \textit{Cosmochrony~2.4$\beta$2} --- foundational document.

  \end{thebibliography}
